\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,amssymb} 
\usepackage{etoolbox}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\title{KopiBoy Chatbot Privacy Policy}
\author{Joseph Matthias Goh}
\makeatletter
\patchcmd{\@maketitle}{\begin{center}}{\begin{flushleft}}{}{}
\patchcmd{\@maketitle}{\begin{tabular}[t]{c}}{\begin{tabular}[t]{@{}l}}{}{}
\patchcmd{\@maketitle}{\end{center}}{\end{flushleft}}{}{}
\makeatother
\date{Last updated: 27 December 2016}           %% By default, LaTeX uses the current date
\begin{document}
\setlength{\parskip}{12pt}
\maketitle



\section{Preamble}

Joseph Goh and Stacy Goh (hereinafter known as "Administrators") operates the 
chatbot found at \url{http://m.me/710981409052173} (hereinafter known as the "Service"/"Services") and it is within our policy 
to respect your privacy regarding any information we may collect about you (hereinafter 
also known as "User") while you are using our provided Services.

This document is a privacy policy ("Privacy Policy") that outlines our policy on
collection, retention and usage of information about and on users who access
the Service.

\section{Service Overview}

Chatbots refer to conversational interfaces which may or may not use artificial
intelligence to process your input/process its output. The Service described herein 
is a chatbot with an artificial intelligence that is designed to allow Users to place
orders for a menu item and collect it at the specified location at the agreed time.

\section{Collection of Information}

When accessing or using our Service, as appropriate, you may be asked to enter your
name, email address, professional resume, credit card information or other details to
help you with your experience. We collect information from you when you use the Service,
perform search settings, place an order, respond to surveys or enter other information
into the message dialog with the Service. Information may be freely provided by you, 
or collected automatically when you access the Service. Failure to provide certain 
information may make it impossible for our Service to provide its function.

For operation and maintenance purposes, our Services and any third party services may
collect information that records interaction with the Service (System logs). Users are
responsible for any information of third parties obtained, published or shared through
the Service and confirm that they have the third party's consent to provide the
information to us.

If you decide to cease using the Service, your data will still be kept for security 
and analytics purposes only.

\section{Storage of Information}

Information collected by us through the Services will be stored on servers owned
by us which are located in Singapore. Third party platforms and service providers
may store information differently and it is your responsibility to read the privacy
policy of each third party platform or service provider to understand how else your 
information may be stored. Usage of third party platforms and service providers will
be disclosed in a reasonably obvious manner to you. 

\section{Processing of Information}

We process your information in a proper manner and shall take appropriate security
measures to prevent unauthorized access, disclosure, modification, or unauthorized
destruction of it.

Information processing is carried out using computers and/or IT enabled tools,
following industry standard procedures and modes strictly related to the purposes
indicated. In addition to ourselves, in some cases, the information may be accessible to
certain types of persons in charge, involved with the operation of the site
(administration, sales, marketing, legal, system administration) or external parties
(such as third party technical service providers, mail carriers, hosting providers,
IT companies, communications agencies) appointed by me, if necessary, as data
processors.

In the case of our hidden third party service providers, information you send to us 
is processed by API.ai (\url{https://api.ai}) and your use of the Service implies 
your consent of our and their respective privacy policies.

The updated list of these parties may be requested from us at any time.

\section{Use of Information}
The information we collect from you when you use features of the Service, is collected
to allow us to provide and improve upon our Services, as well as for the following
purposes:

\begin{enumerate}
\item{To personalize your experience and to allow us to contact you and to deliver
the type of content and product offerings in which you are most interested;} 
\item{To improve the Service in order to better serve you;} 
\item{To provide access to/from accounts with third party services;}
\item{To administer a contest, promotion, survey or other feature;} 
\item{To quickly process your transactions;}
\item{To follow up with you after correspondence.}
\end{enumerate}

Your information will never be shared with third parties without your consent.

\section{Protection of Information}

We disclose potentially personally-identifying and personally-identifying information
only to those of our employees, contractors and affiliated organizations that (i) need
to know that information in order to process it on our behalf or to provide Services made
available by us, and (ii) that have agreed not to disclose it to others. Some of those
employees, contractors and affiliated organizations may be located outside of your
home country; by using the Service, you consent to the transfer of such information
to them.

We will not rent or sell potentially personally-identifying and personally-identifying
information to anyone. Other than to our employees, contractors and affiliated
organizations, as described above, we disclose potentially personally-identifying and
personally-identifying information only in response to a subpoena, court order or
other governmental request, or when we believe in good faith that disclosure is
reasonably necessary to protect the property or rights of Administrators, third parties 
or the public at large. If you are a user of our Services and have supplied
your email address, we may occasionally send you an email to tell you about new
features, solicit your feedback, or just keep you up to date with what’s going on
with the Service. We primarily use our various product blogs to communicate this type
of information, so we expect to keep this type of email to a minimum. If you send us
a request (for example via a support email or via one of our feedback mechanisms),
we reserve the right to publish it in order to help us clarify or respond to your
request or to help us support other users.

We take all measures reasonably necessary to protect against the unauthorized access,
use, alteration or destruction of potentially personally-identifying and
personally-identifying information.

\section{Aggregated Statistics}

We may collect statistics about the behavior of our Users. For instance, we may 
use spam screened by the third party services or Administrators to help identify spam
and we may display this information publicly or provide it to others. However, we do 
not disclose personally-identifying information other than as described above.

\section{Business Transfers}

In the unlikely event that the Service is acquired, User information would
be one of the assets that is transferred or acquired by a third party. You acknowledge
that such transfers may occur, and that any acquirer of the Service may continue to use
your personal information as set forth in this policy.

\section{Privacy Policy Changes}

Although most changes are likely to be minor, we may change this Privacy Policy from
time to time, and at our sole discretion. We encourage visitors such as yourself to
frequently check this page for any changes to this Privacy Policy. Your continued use of
our Services after any change in this Privacy Policy will constitute your acceptance of
such change.

\section{Contact Us}

If there are any questions, concerns, possible improvements or complaints regarding
this Privacy Policy, you can contact us via the KopiBoy app at \url{http://m.me/710981409052173}

\section{Acknowledgements}

This Policy is an adaptation of Automattic's Privacy Policy which you can find
at the URL, \url{https://automattic.com/privacy/}, and is likewise licensed under the
\textbf{Creative Commons Sharealike 4.0} license.


\end{document}