\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,amssymb} 
\usepackage{etoolbox}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\title{KopiBoy Chatbot Terms of Service}
\author{Joseph Matthias Goh}
\makeatletter
\patchcmd{\@maketitle}{\begin{center}}{\begin{flushleft}}{}{}
\patchcmd{\@maketitle}{\begin{tabular}[t]{c}}{\begin{tabular}[t]{@{}l}}{}{}
\patchcmd{\@maketitle}{\end{center}}{\end{flushleft}}{}{}
\makeatother
\date{Last updated: 27 December 2016}           %% By default, LaTeX uses the current date
\begin{document}
\setlength{\parskip}{12pt}
\maketitle



\section{Preamble}

Joseph Goh and Stacy Goh ("Administrators") operates the chatbot found at 
\url{http://m.me/710981409052173} (hereinafter known as the "Service"/"Services").

This document outlines a Terms of Service ("Term", "Terms") agreement and your access to and use of the Service is 
conditioned on your acceptance of and compliance with these Terms. These Terms apply to all visitors, 
users and others who access or use the Service.

By accessing or using the Service you agree to be bound by these Terms. If you disagree with
any part of the terms then you may not access the Service.

\section{Termination}

We may terminate or suspend access to our Service immediately, without prior notice or liability,
for any reason whatsoever, including without limitation if you breach the Terms.

All provisions of the Terms which by their nature should survive termination shall survive
termination, including, without limitation, ownership provisions, warranty disclaimers, indemnity
and limitations of liability.

\section{Links To Other Web Sites}

Our Service may contain links to third­party web sites or services that are not owned or controlled
by the Administrators.

The Administrators has no control over, and assumes no responsibility for, the
content, privacy policies, or practices of any third party web sites or services. You further
acknowledge and agree that the Administrators shall not be responsible or liable,
directly or indirectly, for any damage or loss caused or alleged to be caused by or in connection
with use of or reliance on any such content, goods or services available on or through any such
web sites or services.

We strongly advise you to read the terms and conditions and privacy policies of any third­party
web sites or services that you visit.

\section{Governing Law}

These Terms shall be governed and construed in accordance with the laws of Singapore, without 
regard to its conflict of law provisions.

Our failure to enforce any right or provision of these Terms will not be considered a waiver of
those rights. If any provision of these Terms is held to be invalid or unenforceable by a court, the
remaining provisions of these Terms will remain in effect. These Terms constitute the entire
agreement between us regarding our Service, and supersede and replace any prior agreements
we might have between us regarding the Service.

\section{Changes}

Although most changes are likely to be minor, we may change the Terms from
time to time, and at our sole discretion. We encourage visitors such as yourself to
frequently check this page for any changes to this document. Your continued use of
our Services after any change in the Terms will constitute your acceptance of
such change.

\section{Contact Us}

If there are any questions, concerns, possible improvements or complaints regarding
this Privacy Policy, you can contact us via the KopiBoy app at \url{http://m.me/710981409052173}

\end{document}